\documentclass{article}

\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage{algorithmicx}
\usepackage{algpseudocode}
\usepackage{amstext}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{chemfig}
\usepackage{wrapfig}
\usepackage{subcaption}
\usepackage{tikz}
\usepackage{pgfplots}
\pgfplotsset{compat=1.18}

\usetikzlibrary{trees}

\bibliographystyle{abbrv}

% aliases
\newcommand{\F}{\mathcal{F}}
\newcommand{\M}{\mathcal{M}}
\newcommand{\T}{\mathbb{T}}

\DeclareMathOperator*{\argmax}{arg\,max}
\DeclareMathOperator*{\argmin}{arg\,min}

\title{Substructure search optimizations}

\begin{document}
\maketitle

\begin{abstract}
Substructure search in chemical compound databases is a fundamental task in cheminformatics with critical implications for fields such as drug discovery, materials science, and toxicology. However, the increasing size and complexity of chemical databases have rendered traditional search algorithms ineffective, exacerbating the need for scalable solutions. This paper introduces a novel approach to enhance the efficiency of substructure search, moving beyond the traditional full-enumeration methods. Our strategy employs a unique index structure: a tree that segments the molecular data set into clusters based on the presence or absence of certain features. This innovative indexing mechanism is inspired by the binary Ball-Tree concept and demonstrates superior performance over exhaustive search methods, leading to significant acceleration in the initial filtering process. Comparative analysis with the existing Bingo algorithm reveals the efficiency and versatility of our approach. Although the current implementation does not affect the verification stage, it has the potential to reduce false positive rates. Our method offers a promising avenue for future research, meeting the growing demand for fast and accurate substructure search in increasingly large chemical databases.
\end{abstract}

%\input{Introduction}
\input{introduction}
\input{algo-pipeline-picture}
\input{algorithm-fb}
\input{benchmarks}
\input{further-development-fb}
%\input{references}

	
\section{Availability of Data and Materials}

The source code and datasets used in this study are openly available in the following repository:

\begin{itemize}
    \item \textbf{Repository Name:} Quantori QTR Fingerprint
    \item \textbf{GitHub Link:} \url{https://github.com/quantori/qtr-fingerprint}
\end{itemize}

The repository contains all the necessary source code, data, and instructions required to replicate the experiments and analyses presented in this paper. This includes scripts for data preprocessing, model training, evaluation, and any additional utilities used in the study.

For further inquiries regarding the data and code, or for assistance with replication efforts, please contact the corresponding author or raise an issue in the GitHub repository.


\bibliography{biblio}

\end{document}
